Fig2

### 2020-04-17 analysis/figure-2.Rmd
now with fig and 2 togetehr

```{r setup, include=FALSE}
library(tidyverse)
library(cowplot)
library(kableExtra) 
library(ggtext) # for italic fonts
library(ggsignif) # fot stats on plots

@@

## DEGs

```{r allDEGs}
DEG_path <- "../results/DEseq2/"   # path to the data
DEG_files <- dir(DEG_path, pattern = "*DEGs") # get file names
DEG_pathfiles <- paste0(DEG_path, DEG_files)
#DEG_files

allDEG <- DEG_pathfiles %>%
  setNames(nm = .) %>% 
  map_df(~read_csv(.x), .id = "file_name") %>% 
  mutate(DEG = sapply(strsplit(as.character(file_name),'./results/DEseq2/'), "[", 2))  %>% 
  mutate(DEG = sapply(strsplit(as.character(DEG),'_diffexp.csv'), "[", 1))  %>% 
  mutate(tissue = sapply(strsplit(as.character(DEG),'\\.'), "[", 1)) %>%
  mutate(down = sapply(strsplit(as.character(DEG),'\\_'), "[", 3)) %>%
  mutate(up = sapply(strsplit(as.character(DEG),'\\_'), "[", 4)) %>%
  mutate(comparison = paste(down,up, sep = "_")) %>%
  mutate(sex = sapply(strsplit(as.character(sextissue),'\\_'), "[", 1)) %>%
  mutate(tissue = sapply(strsplit(as.character(sextissue),'\\_'), "[", 2)) %>%
dplyr::select(sex,tissue,comparison, direction, gene, lfc, padj, logpadj) 
head(allDEG)

allDEG$tissue <- factor(allDEG$tissue , levels = tissuelevel)
allDEG$comparison <- factor(allDEG$comparison , levels = comparisonlevels)
allDEG$direction <- factor(allDEG$direction, levels = charlevels)
```

@@

makebargraph <- function(whichtissue, myylab, lowlim, higherlim){
  p <- allDEG %>%
    filter(tissue == whichtissue,
           comparison != "control_bldg") %>%
  ggplot(aes(x = comparison,  fill = direction)) +
    geom_bar(position = "dodge") +
    facet_grid(tissue~sex) +
    theme_B3() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          legend.position = "none")  +
    guides(fill = guide_legend(nrow = 1)) +
    labs(x = "Sequential parental care stage comparisons", 
         y = myylab,
         subtitle = " ") +
  scale_fill_manual(values = allcolors,
                       name = " ",
                       drop = FALSE) +
  scale_color_manual(values = allcolors) +
  geom_text(stat='count', aes(label=..count..), vjust =-0.5, 
            position = position_dodge(width = 1),
            size = 2, color = "black")  +
  ylim(lowlim, higherlim)
  return(p)
}

# hyp
p1 <- makebargraph("hypothalamus","DEGs", 0, 1250) + theme(axis.text.x = element_blank(), 
                                                               axis.title.x = element_blank())
# pit
p2 <- makebargraph("pituitary","DEGs", 0, 1250)  +  theme(axis.text.x = element_blank(), axis.title.x = element_blank(), 
                                                              strip.text.x = element_blank())
# gon
p3 <- makebargraph("gonad","DEGs", 0, 1250) +  theme(strip.text.x = element_blank())
bcd <- plot_grid(p1,p2,p3, nrow = 3, rel_heights = c(1.2,1,1.5), labels = c("b", "c", "d"), label_size = 8)

expdesign <- png::readPNG("../figures/images/fig_fig2a.png")
expdesign <- ggdraw() +  draw_image(expdesign, scale = 1)

plot_grid(expdesign, bcd, labels = c("a", " "), label_size = 8, nrow = 2, rel_heights = c(0.25,1))

@@

write.csv(allDEG, "../../musicalgenes/data/allDEG.csv")

>>>>

## this file no longer works!

The code here is incomplete. Saving it to use for creating tables.

```{r setup, include=FALSE}

@@

@@

@@

#write.csv(allDEG, "../../musicalgenes/data/allDEG.csv")
